\documentclass[10pt]{article}
\usepackage[landscape,margin=0.45in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[table]{xcolor}
\usepackage{array,tabularx,booktabs,multirow}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{ragged2e}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}
\lhead{BDATA 200}
\rhead{Live Presentation Evaluation Sheet}
\cfoot{\thepage/\pageref{LastPage}}

\definecolor{uwpurple}{HTML}{4B2E83}
\definecolor{uwgold}{HTML}{B7A57A}
\definecolor{lightbg}{HTML}{F7F5F1}

\setlength{\headheight}{14pt}
\renewcommand{\arraystretch}{1.2}

\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
\newcolumntype{C}[1]{>{\Centering\arraybackslash}m{#1}}

% Empty outlined stars with more spacing so they do not overlap
\newcommand{\ratingstars}{%
\begin{tikzpicture}[baseline=-0.6ex, x=1cm, y=1cm]
  \foreach \x in {0,0.95,1.90,2.85,3.80}{
    \node[
      star,
      star points=5,
      star point ratio=2.25,
      draw=uwgold,
      line width=0.6pt,
      fill=white,
      minimum size=0.42cm,
      inner sep=0pt
    ] at (\x,0) {};
  }
\end{tikzpicture}%
}

\begin{document}
\thispagestyle{fancy}

\begin{center}
    {\Large\bfseries\color{uwpurple} BDATA 200 Live Presentation Evaluation Sheet}\\[2pt]
    {\normalsize\color{uwgold} Project 1: Kaggle Competition Dataset}
\end{center}

\noindent
\colorbox{lightbg}{%
\parbox{\dimexpr\linewidth-2\fboxsep\relax}{%
\small
\textbf{Project Title:} \rule{0.32\linewidth}{0.4pt}\hfill
\textbf{Group Name:} \rule{0.20\linewidth}{0.4pt}\hfill
\textbf{Date:} \rule{0.12\linewidth}{0.4pt}\\[0.5em]
\textbf{Student(s):} \rule{0.78\linewidth}{0.4pt}
}}

\vspace{0.4em}
\noindent\small\textit{Directions:} Mark the stars during the presentation. This rubric focuses on the \textbf{live presentation} criteria from the project guidelines: project background, question, methods, results, storytelling, discussion, and delivery.

\vspace{0.45em}
\rowcolors{2}{white}{lightbg}
\small
\begin{tabularx}{\linewidth}{|>{\RaggedRight\arraybackslash}m{0.23\linewidth}|C{0.07\linewidth}|C{0.19\linewidth}|Y|}
\hline
\rowcolor{uwpurple}
\color{white}\textbf{Criterion} & \color{white}\textbf{Weight} & \color{white}\textbf{Rating} & \color{white}\textbf{What to Look For} \\
\hline
Project Background \& Motivation & 10\% & \ratingstars & Explains the context of the project and why the audience should care. \\
\hline
Research Question / Objective & 15\% & \ratingstars & The question is clear, specific, interesting, and worth investigating. \\
\hline
Methods \& Data & 15\% & \ratingstars & Describes the dataset, cleaning, and analytical approach clearly. \\
\hline
Results \& Visualization & 20\% & \ratingstars & Presents key findings effectively and includes at least one strong visualization. \\
\hline
Insights \& Surprise & 15\% & \ratingstars & Uses evidence to challenge assumptions or reveal something unexpected. \\
\hline
Storytelling \& Narrative Arc & 15\% & \ratingstars & Follows a compelling structure: setup $\rightarrow$ data reveal $\rightarrow$ insight. \\
\hline
Discussion \& Broader Context & 5\% & \ratingstars & Interprets findings in a larger societal, cultural, historical, political, or ethical context. \\
\hline
Delivery \& Q\&A & 5\% & \ratingstars & Professional delivery, clear communication, and thoughtful Q\&A participation. \\
\hline
\rowcolor{uwgold!18}
\textbf{Total} & \textbf{100\%} & & \\
\hline
\end{tabularx}

\vspace{0.45em}
\noindent\begin{minipage}[t]{0.64\linewidth}
\textbf{Instructor Notes:}\\[0.25em]
\fbox{\parbox[c][1.45in][t]{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}{\vspace{0.15em}}}
\end{minipage}\hfill
\begin{minipage}[t]{0.33\linewidth}
\small
\textbf{Quick scoring guide}\\[0.2em]
1 star = weak\\
2 stars = developing\\
3 stars = satisfactory\\
4 stars = strong\\
5 stars = excellent
\end{minipage}

\end{document}